Corona of an M7 fast rotator with a high latitude flare

### 2023-04-19 src/tex/ms.tex
[showyourwork] overleaf sync

\begin{figure}[ht!]
    \script{FIGURE_data_resid.py}
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/pn_onlyflare1_data_resid.png}
        \caption{
         Flare only PN Double apec spectrum fit.
        }
        \label{fig:spec_pn_onlyflare}
    \end{centering}
\end{figure}

\begin{figure}[ht!]
    \script{FIGURE_data_resid.py}
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/joint_onlyflare_data_resid.png}
        \caption{
         Flare only joint Double APEC spectrum fit.
        }
        \label{fig:spec_joint_onlyflare}
    \end{centering}
\end{figure}

\begin{figure}[ht!]
    \script{FIGURE_data_resid.py}
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/joint_noflare_data_resid.png}
        \caption{
         Joint Double APEC spectrum fit with flare excluded.
        }
        \label{fig:spec_joint_noflare}
    \end{centering}
\end{figure}

\begin{figure}[ht!]
    \script{FIGURE_data_resid.py}
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/joint_all_data_resid.png}
        \caption{
         Joint Double APEC spectrum fit.
        }
        \label{fig:spec_joint_all}
    \end{centering}
\end{figure}

>>>>

\begin{figure}
    \script{FIGURE_data_resid.py}
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/pn_onlyflare_data_resid.png}
        \caption{
         Flare only PN Double apec spectrum fit.
        }
        \label{fig:spec_pn_onlyflare}
    \end{centering}
\end{figure}

\begin{figure}
    \script{FIGURE_data_resid.py}
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/pn_onlyflare_data_resid.png}
        \caption{
         No flare PN Double apec spectrum fit.
        }
        \label{fig:spec_pn_noflare}
    \end{centering}
\end{figure}

\begin{figure}
    \script{FIGURE_data_resid.py}
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/pn_data_resid.png}
        \caption{
         PN Double apec spectrum fit.
        }
        \label{fig:spec_pn}
    \end{centering}
\end{figure}

\begin{figure}
    \script{FIGURE_data_resid.py}
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/mos1_data_resid.png}
        \caption{
         MOS1 Double apec spectrum fit.
        }
        \label{fig:spec_mos1}
    \end{centering}
\end{figure}

\begin{figure}
    \script{FIGURE_data_resid.py}
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/mos2_data_resid.png}
        \caption{
         MOS2 Double apec spectrum fit.
        }
        \label{fig:spec_mos2}
    \end{centering}
\end{figure}

\begin{figure}
    \script{FIGURE_data_resid.py}
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/joint_onlyflare_data_resid.png}
        \caption{
         Flare only joint Double APEC spectrum fit.
        }
        \label{fig:spec_joint_onlyflare}
    \end{centering}
\end{figure}

\begin{figure}
    \script{FIGURE_data_resid.py}
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/joint_noflare_data_resid.png}
        \caption{
         Joint Double APEC spectrum fit with flare excluded.
        }
        \label{fig:spec_joint_noflare}
    \end{centering}
\end{figure}

\begin{figure}
    \script{FIGURE_data_resid.py}
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/joint_all_data_resid.png}
        \caption{
         Joint Double APEC spectrum fit.
        }
        \label{fig:spec_joint_all}
    \end{centering}
\end{figure}
